Which of my Transient Type Checks are not (Almost) Free?

### 2019-09-11 paper.tex
Edits sec. 3.3
Signed-off-by: Stefan Marr <git@stefan-marr.de>

\subsection{Experimental Set Up}
As in our previous work \cite{roberts-and-co-ecoop-2019} which used the same set of benchmarks, to account for the complex warmup behaviour of modern systems \citep{Barrett:2017:VMW} as well as
the non-determinism caused by \eg garbage collection and cache effects, we ran each benchmark for 1000 iterations in the same invocation of Moth, and discard the first 350 iterations to ignore warmup JIT compilation.

@@

In our previous work we also compared the performance of untyped code on Moth against state-of-the-art VMs: Java, Node.js using the V8 JavaScript VM, and the Higgs JavaScript VM. Java was the fastest of these, and on average V8 was about 1.8x slower than Java, Moth was 2.3x slower, and Higgs was 10.4x slower.
Hence we continue to argue that ``Moth is a suitable platform to assess the impact of our approach to gradual type checking, because its performance is close enough to state-of-the-art VMs, and run-time overhead is not hidden by slow baseline performance.''

>>>>

\subsection{Experimental Set Up}
To account for the complex warmup behaviour of modern systems \citep{Barrett:2017:VMW} as well as
the non-determinism caused by \eg garbage collection and cache effects, we ran each benchmark for 1000 iterations in the same invocation of Moth, and discard the first 350 iterations to ignore warmup JIT compilation.

@@

In previous work \cite{roberts-and-co-ecoop-2019}, we also compared the performance of untyped code on Moth against state-of-the-art VMs: Java, Node.js using the V8 JavaScript VM, and the Higgs JavaScript VM. Java was the fastest of these, and on average V8 was about 1.8x slower than Java, Moth was 2.3x slower, and Higgs was 10.4x slower.
We believe, this makes Moth suitable for assessing the impact of type checking,
because Moth's performance is close enough to state-of-the-art VMs,
which avoids hiding of type check overheads in a slow baseline.
